---
title: "Vignette Title"
author:
- name: Daniel Van Twisk
  affiliation: Roswell Park Comprehensive Cancer Center
- name: Martin Morgan
  affiliation: Roswell Park Comprehensive Cancer Center
  email: maintainer@biocondcutor.org
package: BiocIO
output:
  BiocStyle::html_document
abstract: |
  BiocIO contains defintions for import and export methods used throughout
  Biocondcutor for IO purposes. The BiocFile class which serves as an interface
  for File classes within Bioconductor is also defined in this package. This
  vignette will describe the functionality of these base methods and classes as
  well as an example for developers on how to interface with them.
vignette: |
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

# Installation

```{r installation, eval=FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install('BiocIO')
```

# Basic use

## Import and Export
The functions import and export load and save objects from and to particular
file formats. The rtracklayer package implements support for a number of
annotation and sequence formats.

```{r basic_import}

```

```{r basic_export}

```

## The BiocFile Class
BiocFile is a base class for high-level file abstractions, where subclasses are
associated with a particular file format/type. It wraps a low-level
representation of a file, currently either a path/URL or connection.

```{r basic_BiocFile}

```

## CompressedFile

```{r basic_CompressedFile}

```

# Example use cases

# For developers


## Session info {.unnumbered}

```{r sessionInfo, echo=FALSE}
sessionInfo()
```
